Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
slides

-   **Efficacy**: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**: Interested in correctly ranking the best competitor as first
:::

@@

-   **Efficacy**[^1]: Final rankings should match the true rankings of the strength of the competitors

>>>>

@@

-   **Efficacy**[^1]: Final rankings should match the true rankings of all the competitors
